Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
More bashing

Labeled boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights. Unless otherwise marked, sequential addresses retain the previous domain,
as hinted by their colors \bcp{where do we see this happening?  Is it
  important?}. Domains are not part of the machine state; rather, they
describe the intended security role of the address
that the enforcement mechanism must adhere to. Such a domain
can be \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), or \(\outside\)
(outside the stack entirely.) These are abbreviated \(U\) and \(S(\dots)\)\bcp{Nope} in the
figures. Global variables and code, which are not shown in the figures, would
also be labeled \(\outside\).  \bcp{what about RetPtr?}
Domains form part of the {\em context} associated with a machine state.
(We will introduce some other parts of the context as needed.)

>>>>

Labeled boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights. Unless otherwise marked, sequential addresses retain the previous domain,
as hinted by their colors \bcp{where do we see this happening?  Is it
  important?}. Domains are not part of the machine state; rather, they
describe the intended security role of the address
that the enforcement mechanism must adhere to. Such a domain
can be \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), or \(\outside\)
(outside the stack entirely.)
% These are abbreviated \(U\) and \(S(\dots)\)\bcp{Nope} in the figures.
Global variables and code, which are not shown in the figures, would
also be labeled \(\outside\).  \bcp{what about RetPtr?}
Domains form part of the {\em context} associated with a machine state.
(We will introduce some other parts of the context as needed.)
